\documentclass{beamer}
\usepackage[spanish,mexico]{babel}
\usepackage{graphicx,hyperref,ru,url}
\usepackage{textpos}
\usepackage{etoolbox}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsbsy}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage[mathscr]{eucal}
\usepackage{fancyhdr}
\usepackage{supertabular}
\usepackage{fancybox}
\usepackage{array}
\usepackage{booktabs}
\usepackage{soul}
\usepackage{epic}
\usepackage{float}
\usepackage{subcaption}
\usepackage{appendix}
% The title of the presentation:
%  - first a short version which is visible at the bottom of each slide;
%  - second the full title shown on the title slide;
\title[Numerical Solutions for Burgers' Equation in the Stochastic and Deterministic Version Using Spectral Methods.]{
  Numerical Solutions for Burgers' Equation in the Stochastic and Deterministic Version Using Spectral Methods.}

% Optional: a subtitle to be dispalyed on the title slide
%\subtitle{Show where you're from}

% The author(s) of the presentation:
%  - again first a short version to be displayed at the bottom;
%  - next the full list of authors, which may include contact information;
\author[Alan Daniel Matzumiya Zazueta]{
  Alan Daniel Matzumiya Zazueta \\\medskip
  {\small \url{alan.matzumiya@gmail.com}}}

% The institute:
%  - to start the name of the university as displayed on the top of each slide
%    this can be adjusted such that you can also create a Dutch version
%  - next the institute information as displayed on the title slide
\institute[Universidad de Sonora]{
  Universidad de Sonora}

% Add a date and possibly the name of the event to the slides
%  - again first a short version to be shown at the bottom of each slide
%  - second the full date and event name for the title slide
\date[\Today]{
  \Today}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}	
	\begin{block}{Motivaci\'on}
	\begin{itemize}
		\only<1->{
			\item 
			Encontrar soluciones anal\'iticas de ecuaciones diferenciales muchas veces es complicado.  
		}
		\only<2->{
			\item 
			Son necesarias para estudiar sistemas complejos. 
		}
		\only<3->{
			\item 
			Los m\'etodos espectrales son una excelente alternativa para obtener aproximaciones de alta precisi\'on. 	
		}
		\only<4->{
			\item 
			Ademas, son faciles de implementar. 	
		}			
	\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\begin{block}{Objetivos}
	\begin{itemize}	
		\only<1->{
		\item 
		Estudiar los fundamentos de los m\'etodos espectrales.
		}
		\only<2->{
		\item
		Implementarlos a la ecuaci\'on de Burgers' en su versi\'on determinista y estoc\'astica.
		}
		\only<3->{
		\item 
		Hacer estudios num\'ericos para evaluar el comportamiento, y la precisi\'on de estos m\'etodos.		
		}
	\end{itemize}
\end{block}
\end{frame}

\begin{frame}
  \frametitle{Contenido}

  \tableofcontents
\end{frame}

% Section titles are shown in at the top of the slides with the current section 
% highlighted. Note that the number of sections determines the size of the top 
% bar, and hence the university name and logo. If you do not add any sections 
% they will not be visible.
\section{Introducci\'on}
	\input{Introduccion}
  
\section{M\'etodos Espectrales}
	\input{Metodos_Espectrales}

\section{Ecuaci\'on de Burgers' Determinista}
\input{Burgers_Determinista}

\section{Ecuaci\'on de Burgers' Estoc\'astica}
  \input{Burgers_Estocastica}

\section{Conclusiones}
  \input{Conclusiones}

\end{document}
