\chapter{Introduction}
\label{Introduction}

	Differential equations, ordinary or partial, allow modeling phenomena that evolve with respect to space and time. They are commonly used to describe the propagation of sound or heat and appear frequently in models related to electrostatics, electrodynamics, fluid dynamics, elasticity, quantum mechanics, and among other more related areas. \\
	
	However, their analytical solutions cannot always be easily obtained and in many cases, it will be necessary to resort to very complex techniques that tend to give solutions with very impractical mathematical expressions to use. In particular, problems characterized as non-linear present these difficulties, and considering a different alternative to find solutions may be a more reasonable option. \\  
	
	There are alternatives to find solutions to differential equations, which depend on the nature of the problem to be solved. For example, computational fluid dynamics is one of the branches of fluid mechanics that uses numerical methods and algorithms to solve and analyze fluid flow problems that perform millions of calculations to simulate the interaction of liquids and gases through complex surfaces. However, even with simplified equations and high-performance supercomputers, in many cases, only approximate results can be achieved. \\
	
	The resolution of differential equations related to the characterization of fluids, and in general, for those that occur in the field of complex systems, are considered of utmost importance since they allow studying problems of great interest such as the turbulence phenomenon that allows understanding with precision its dynamics. Understanding these phenomena through differential equations is not enough, it is also necessary to characterize their nature, which in some cases is possible if the dimensionless value of the Reynolds number ($Re$) that indicates whether a fluid follows a laminar flow is known or turbulent. However, it is not always possible to predict with this information those phenomena that present turbulence in a combination of convection or combustion processes, and that therefore require greater attention in their dynamics. \\
	
	Spectral methods have recently emerged as a viable alternative for the numerical solution of partial differential equations. They have proved particularly useful in fluid dynamics simulation where are now regularly used large spectral hydrodynamics codes to study turbulence, numerical weather prediction, ocean dynamics, and any other problems where high accuracy is desired. \\
	
	Due to the above, he has motivated the development of this thesis by studying spectral methods extensively to acquire the ability to use this tool and understand them from the point of view of mathematical analysis. To develop this study we will focus first on the elementary theory of these methods, encompassing enough knowledge to allow us to develop, implement and analyze under this approach a wide variety of problems that arise in the partial differential equations that evolve. \\
	
	To understand the application of these methods, the well-known Burgers' equation has been considered, since it is an ideal problem for understanding these methods because, in addition to being a non-linear problem that presents interesting characteristics, it can be useful to develop the ability to attack more complex problems. Furthermore, in order to extend the study of the implementation of spectral methods, we are going to work with the stochastic version of this equation that will be very useful for us to know in general terms trying to solve problems of this type, which are considered of great importance for its wide field of applications and that it is still an area that is in full development due to the great difficulty in obtaining solutions. \\
	
	To carry out this study, we will divide the work into six parts organized as follows
	\begin{enumerate}
		\item[1.] In chapter \ref{Introduction}, a brief history of Burgers' equation will be presented in its deterministic version, and we will also present how to obtain the analytical solution for an initial value problem of this equation, transforming it into another linear one that can be solved using the Fourier transform. Later, the origin of the stochastic version will be discussed, in addition to its importance within mathematics and physics.
		
		\item[2.] In chapter \ref{Chapter_2}, we will study the theoretical bases of spectral methods using the well-known Fourier series as the main tool, which will allow us to study a theory of approximation of functions under two approaches, using orthogonal projections and another using interpolation techniques. These two approaches will be examined independently, studying their implementation and some theoretical results that will be useful in chapter \ref{Chapter_3}.  
		
		\item[3.] In chapter \ref{Chapter_3}, the spectral methods known as Fourier-Galerkin and Fourier-Collocation will be developed using the tools examined in chapter \ref{Chapter_2}, verifying their convergence theory. For this, the deterministic Burgers' equation will be used, taking advantage of its linearized form to describe the methods, which will then be applied to the original nonlinear equation to describe the algorithms of its computational implementation that will allow us to perform numerical experiments and to be able to observe some characteristics interesting for your discussion.
		
		\item[4.] In chapter \ref{Chapter_4}, a spectral method used to solve stochastic partial differential equations that was studied in \cite{Delgado2016} will be disclosed in as much detail as possible. We will see that this method, which is built based on the well-known Hermite polynomials, will allow us to obtain solutions of stochastic problems by solving a deterministic type problem, and will be illustrated using the stochastic Burgers' equation developing its implementation and also numerical simulations.
		
		\item[5.] In this last chapter, we will discuss the most relevant of each chapter, and we will give some observations of the obtained numerical results to conclude with some ideas that can be considered to extend this work.
		
		\item[6.] At the end of this work, an appendix \ref{Appendix_A} was added, which will be useful to understand in more detail the spectral method developed in chapter \ref{Chapter_4}.
	\end{enumerate}
	
	\input{introduction/Burgers_Deterministic}
	\newpage
	\input{introduction/Burgers_Stochastic}
